Copy number inference with InferCNV

### 2024-05-20 analyses/cell-type-ewings/exploratory_analysis/04-infercnv.Rmd
add some more comments to main exploratory notebook

reference_cells_only <- all_cnv_df |> 
  dplyr::filter(stringr::str_detect(subcluster, "reference")) |> 
  dplyr::mutate(has_cnv = NA,
                z_scaled_cnv = NA)

@@

>>>>

# don't include the normal cells that were provided as reference in scaling 
reference_cells_only <- all_cnv_df |> 
  dplyr::filter(stringr::str_detect(subcluster, "reference")) |> 
  dplyr::mutate(has_cnv = NA,
                z_scaled_cnv = NA)

@@

In the below plot we label all non-reference cells as either tumor or normal. 
Cells that are NA are those that were already classified as reference cells.
